### 2020-01-11 docs/build/assets/Components/components.tex
Added assets for docs.

\def\lw{2mm}        % Arrow line width
\def\mw{2cm}        % Minimum width of component
\def\mh{1.75cm}     % Minimum height of component
\def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=2cm, minimum height=1.5cm, thick
    },
    pics/Component/.style n args = {2}{
        code = {
            \node [border, align=center](-edge){#1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        % Place the blocks 
        \draw pic (b1) {Component={Static\\System}{t}};
        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
        % Glow the blocks
        \drawshadowbis{b1-edge};
        \drawshadowbis{b2-edge};
        \drawshadowbis{b3-edge};
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
            \draw[->] (b1-edge.east) -- (b2-edge.west);
            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
            \draw[->] (a) -- ++(0.5cm, 0cm);
            \draw[->] (a) |- (b3-edge.east);
            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
            \draw[-] ([yshift=0.75mm] b) |- (b3-edge.west);
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\def\lw{1mm}        % Arrow line width
\def\mw{2cm}        % Minimum width of component
\def\mh{1.75cm}     % Minimum height of component
\def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=2.5cm, minimum height=2cm, thick
    },
    pics/Component/.style n args={3}{
        code = {
            \node [border, align=center](-edge){#1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
            \draw (-edge.south) node [yshift=-0.75*\mh, align=left, font=\large] {#3};
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font={\large}}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = 0.5cm, 
            nodes={anchor=center}]{
        \draw pic (b1) {Component={Source}{t}{$y=g(t)$}};    
        \& 
        \draw pic (b3) {Component={Sink}{t}{}};  
        \&
        \draw pic (b5) {Component={StaticSystem}{t}{$y=g(u, t)$}};    
        \\
        \draw pic (b9) {Component={DiscreteSistem}{k}{$x_{k+1}=f(x_k, u_k, k)$\\$\hspace*{0.4cm}y_k=g(x_k, u_k, k)$}};
        \& 
        \draw pic (b7) {Component={ODESystem}{t}{$\dot{x}=f(x,u,t)$\\$y=g(x,u,t)$}};
        \& 
        \draw pic (b2) {Component={DAESystem}{t}{$0=f(dx,x,u,t)$\\$y=g(x,u,t)$}}; 
        \\
        \draw pic (b4) {Component={RODESystem}{t}{$dx=f(x,u,t,W_t)dt$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
        \& 
        \draw pic (b6) {Component={SDESystem}{t}{$dx=f(x,u,t)dt+h(x,u,t)dW_t$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
        \&
        \draw pic (b8) {Component={DDESystem}{t}{$\dot{x}=f(x,x_\tau,u,t)$\\$y=f(x,u,t)$}}; 
        \\
        };
        % Glow the blocks
        \foreach \x in {1, 2, ..., 9}{
            \drawshadowbis{b\x-edge};
        }
        \begin{scope}[line width=\lw, >={Triangle[width=2mm,length=2mm]}]
            \foreach \x in {1, 2, 4, 5, 6, 7, 8, 9}{
                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(0.5cm, 0cm) node[anchor=west]{$y$};
            }
            \foreach \x in {2, 3, 4, 5, 6, 7, 8, 9}{
                \draw[line width = \lw, ->] ([xshift=-0.5cm] b\x-edge.west) node[anchor=east]{$u$} -- (b\x-edge.west);
            }
        \end{scope}
    \end{tikzpicture}
\end{document}

### 2020-01-11 docs/src/assets/Model/model.tex
Added assets for docs.

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage[utf8]{inputenc}
\usepackage{tikz}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center
    },
    Component/.pic = {
        \node [border, font=\large](-edge){#1}; 
        \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
        \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
        \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {T}; 
    },
}

@@

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\large}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = 0.25cm, nodes={anchor=center}]{
             \& \draw pic (kaynak2) {Component={Source II}}; \& \&   \\[-1cm]
            \draw pic (kaynak1) {Component={Source I}};    \& \& \draw pic (statiksistem1) {Component={StaticSystem I}}; \& \draw pic (statiksistem2) {Component={StaticSystem II}}; \\
            \draw pic (kutuk1) {Component={Sink I}}; \& \& \& \draw pic (kutuk2) {Component={Sink II}}; \\
        };
        % Glow the blocks
        \foreach \x in {kaynak1, kaynak2, kutuk1, kutuk2, statiksistem1, statiksistem2}{
            \drawshadowbis{\x-edge};
        }
        % Draw connections 
        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
            \draw[-] (kaynak1-edge.east) -- ++(0.75cm, 0cm) coordinate(a);
            \draw[->] ([yshift=1mm] a) |- (kutuk1-edge.east);
            \draw[->] (a) |- ([yshift=-0.25cm] statiksistem1-edge.west);
            \draw[-] (kaynak2-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
            \draw[->] ([yshift=1mm] b) |- ([yshift=0.25cm] statiksistem1-edge.west);
            \draw[->] (statiksistem1-edge.east) |- (statiksistem2-edge.west);
            \draw[-] (statiksistem2-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
            \draw[->] ([yshift=1mm] c) |- (kutuk2-edge.east);
        \end{scope}

        % Draw rectangle for subsystem 
        \draw[thick, dashed] ([xshift=-0.25cm, yshift=0.25cm] kaynak2-edge.north west) rectangle ([xshift=0.25cm, yshift=-0.75cm] statiksistem2-edge.south east);
        \draw (statiksistem2-edge.north west) node[yshift=1.75cm, xshift=1cm]{SubSystem};

        % \Place clock 
        \begin{scope}[shift={(-5.75cm, -4.5cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] ([xshift=-0.75*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=0.5*\mw, yshift=1.5*\mh] statiksistem2-edge.north east);
        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=6*\mw]{Model};
    \end{tikzpicture}
\end{document}

>>>>

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage{tikz}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center
    },
    Component/.pic = {
        \node [border](-edge){#1}; 
        \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
        \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
        \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {T}; 
    },
}

@@

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\large}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -1cm]{
                                            \& \draw pic (b1) {Component={B1}}; \&                                  \\
        \draw pic (b2) {Component={B2}};    \&                                  \& \draw pic (b3) {Component={B3}}; \\
                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[1.25cm]
                                            \& \draw pic (b5) {Component={B5}}; \&                                  \\
        };
        % Glow the blocks
        \foreach \x in {1, 2, 3, 4, 5}{
            \drawshadowbis{b\x-edge};
        }
        % Draw connections 
        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
            \def\shiftamount{0.5mm};
            \draw[-] (b2-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
            \draw[-] (a) -- node[midway, anchor=west]{L1} ++(0, 0.5*\mh) coordinate(b);
            \draw[-] (a) -- node[midway, anchor=west]{L2} ++(0cm, -0.5*\mh) coordinate(c);
            \draw[->] (b) |- (b1-edge.west);
            \draw[->] (c) |- ([yshift=0.25cm] b4-edge.west);
            \draw[-] (b1-edge.east) -- ++(0.4*\mw, 0cm) coordinate(d);
            \draw[-] (b4-edge.east) -- ++(0.4*\mw, 0cm) coordinate(e);
            \draw[-] ([yshift=1mm] d) -- node[midway, anchor=east]{L3} ++(0cm, -0.7*\mh) coordinate(f);
            \draw[-] ([yshift=-1mm] e) -- node[midway, anchor=east]{L4} ++(0cm, 0.7*\mh) coordinate(g);
            \draw[->] ([yshift=\shiftamount] f) |- ([yshift=2mm] b3-edge.west);
            \draw[->] ([yshift=-\shiftamount] g) |- ([yshift=-2mm] b3-edge.west);
            \draw (b5-edge.west) -- ++(-1cm, 0cm) coordinate (h);
            \draw[->] ([yshift=-1mm] h) |- node[midway, anchor=east, yshift=-1.25cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
            \draw[->] ([yshift=1mm] g) |- node[midway, anchor=east, yshift=1.25cm]{L5} (b5-edge.east);
        \end{scope}

        % \Place clock 
        \begin{scope}[shift={(-4.25cm, -4cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2*\mw, yshift=0.25*\mh] b1-edge.north east);
        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.4*\mw]{Model};
    \end{tikzpicture}
\end{document}
